Microlensing as a possible probe of the internal structure of quasars

### 2014-04-17 paper1/ms.tex
.
small edits

\author[I. Mohammed et al.] {Irshad Mohammed\thanks{irshad@physik.uzh.ch}$^1$,
Mihai Tomozeiu$^1$, Manuel Rabold$^1$,
\newauthor
Prasenjit Saha,$^1$ and Joachim Wambsgans$^2$\\
$^1${Institute for Theoretical Physics, University of Z$\ddot{u}$rich, 8057 Z$\ddot{u}$rich Switzerland}\\
$^2${University of Heidelberg, Germany}
}

>>>>

\author[Various authors]{[Order TBD]Irshad Mohammed,$^1$ Mihai Tomozeiu$^2$, Manuel Rabold$^2$,
\newauthor
Prasenjit Saha,$^1$ and Joachim Wambsgans$^3$\\
$^1${Physik-Institut, University of Zurich, Winterthurerstrasse 190,
  8057 Zurich, Switzerland} \\
$^2${Institute for Computational Science, University of Zurich,
  Winterthurerstrasse 190, 8057 Zurich, Switzerland} \\
$^3${Zentrum f\"ur Astronomie der Universi\"at Heidelberg,
  M\"onchhofstrasse 12--14, 69120 Heidelberg, Germany}
}

### 2014-04-17 paper1/theory.tex
small edits

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/figure_rhalf.eps}
\caption{\label{fig:lightcurve_crescent} Geometry of crescent sources.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/4rn_magnification.eps}
\caption{\label{fig:lightcurve_crescent} Lightcurves of backwards crescents with  a = 0.3 $R_p$.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/figure_rhalf.eps}
\caption{\label{fig:geom_crescent} Geometry of crescent sources.}
\end{figure}

@@

\begin{figure}
\includegraphics[width = .8\textwidth]{plots/4rn_magnification.eps}
\caption{\label{fig:lightcurve_crescent_back} Lightcurves of backwards crescents with  a = 0.3 $R_p$.}
\end{figure}
